Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-07 snTomas.tex

For Type Ia SNe, the SALT2 model has two additional parameters that
control the shape ($x_1$) and color ($c$) of the light curve.  We use
conservative priors here, defined to encompass a range of Type Ia SN
shapes and colors that is broader than typically allowed in
cosmological analyses \citep[see
e.g.,][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
a bifurcated Gaussian distribution with mean $\bar{x}_1=0$, dispersion
$\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The prior for the
color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
$\sigma_c^+=0.54$ using the same distribution as for $x_1$.  The $c$ parameter in SALT2 combines intrinsic SN
color and extinction due to dust, so the large red tail of this
distribution allows for the possibility of several magnitudes
of dust extinction along the \tomas\ line of sight.

@@

\noindent This inferred magnification is reported in the final column of
Table~\ref{tab:MeasuredMagnification}.

@@

\change{
In general, free-form methods tend to explore the model parameter
space more fully than parametric methods.  This is reflected in the
size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
GRALE, which has the largest, and possibly the most realistic
uncertainties is able to account for mass sheet degeneracy by
introducing a free parameter in the reconstruction that represents an
arbitrarily positioned mass sheet, with normalization to be chosen by
the genetic algorithm.  More complex degeneracies are also accounted
for in GRALE through the use of basis
functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} }

@@

\change{
Nevertheless, one might suppose that a bias could be introduced if we
have adopted incorrect values for the color correction parameter
$\beta$ or extinction law $R_V$ in the SALT2 and MLCS2k2 fits,
respectively.  The appropriate value to use for this color correction
and how it affects inferences about the intrinsic scatter in Type Ia
SN luminosities is a complex question that is beyond the scope of this
work \citep[see
e.g.][]{Marriner:2011,Chotard:2011,Kessler:2013,Scolnic:2014a}.
However, we can already rule this out as a solution for the
magnification discrepancy.  Our error on the \tomas\ distance modulus
already includes an uncertainty in the extinction law and a related
error to account for the intrinsic luminosity scatter. These are well
vetted paraemeters, based on observations of $\sim500$ SNe extending
to $z\sim1.5$ \citep{Sullivan:2011}.  Furthermore, there is no reason
to propose that SN \tomas\ is uniquely affected by a peculiar type of
dust.  Thus, any change in the color correction applied to SN \tomas\
would require the same adjustment to be applied to the unlensed SNe at
similar redshift that make up our comparison sample, largely negating
the effect on the inferred magnification.  }

>>>>

For Type Ia SNe, the SALT2 model has two additional parameters that
control the shape ($x_1$) and color ($c$) of the light curve.  We use
conservative priors here, defined to encompass a range of Type Ia SN
shapes and colors that is broader than typically allowed in
cosmological analyses \citep[see
e.g.,][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
a bifurcated Gaussian distribution with mean $\bar{x}_1=0$, dispersion
$\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The prior for the
color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
$\sigma_c^+=0.54$, using the same distribution as for $x_1$.  The $c$ parameter in SALT2 combines intrinsic SN
color and extinction due to dust, so the large red tail of this
distribution allows for the possibility of several magnitudes
of dust extinction along the \tomas\ line of sight.

@@

\noindent The inferred magnifications for the two different fitters are reported in the final column of
Table~\ref{tab:MeasuredMagnification}.

@@

\change{
In general, free-form methods tend to explore the model parameter
space more fully than parametric methods.  This is reflected in the
size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
GRALE(Williams?), which has the largest, and possibly the most realistic
uncertainties is able to account for mass sheet degeneracy by
introducing a free parameter in the reconstruction that represents an
arbitrarily positioned mass sheet, with normalization to be chosen by
the genetic algorithm.  More complex degeneracies are also accounted
for in GRALE(Williams?) through the use of basis
functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} }

@@

\change{
Nevertheless, one might suppose that a bias could be introduced if we
have adopted incorrect values for the color correction parameter
$\beta$ or extinction law $R_V$ in the SALT2 and MLCS2k2 fits,
respectively.  The appropriate value to use for this color correction
and how it affects inferences about the intrinsic scatter in Type Ia
SN luminosities is a complex question that is beyond the scope of this
work \citep[see
e.g.][]{Marriner:2011,Chotard:2011,Kessler:2013,Scolnic:2014a}.
However, we can already rule this out as a solution for the
magnification discrepancy.  Our error on the \tomas\ distance modulus
already includes an uncertainty in the extinction law and a related
error to account for the intrinsic luminosity scatter. These are well
vetted parameters, based on observations of $\sim500$ SNe extending
to $z\sim1.5$ \citep{Sullivan:2011}.  Furthermore, there is no reason
to propose that SN \tomas\ is uniquely affected by a peculiar type of
dust.  Thus, any change in the color correction applied to SN \tomas\
would require the same adjustment to be applied to the unlensed SNe at
similar redshift that make up our comparison sample, largely negating
the effect on the inferred magnification.  }
